\SW: I. Crowd-sourcing the Discovery of Gravitational Lenses

### 2015-04-21 doc/sw-system.tex
Updated conclusions and abstract, closes #100

We describe \SW, a novel gravitational lens discovery service that yields samples
of high purity and completeness through crowd-sourced visual inspection.
Carefully produced colour composite images are displayed to volunteers via a
classification interface which records their estimates of the positions of
candidate lensed features. Simulated lenses, and expert-classified images which lack lenses,
are inserted into the image stream at random intervals; this training set is
used to give the volunteers feedback on their performance, as well as to
calibrate it in order to allow dynamical updates to the probability of any image
they classify to contain a lens. Low
probability systems are retired from the site periodically, concentrating the
sample towards a set of candidates. Having divided 160 square degrees of
Canada-France-Hawaii Telescope Legacy Survey (\cfhtls)
imaging into some 430,000 overlapping 84 by 84 arcsecond tiles and
displaying them on the site, we were joined by around 37,000 volunteers who
contributed 11~million image classifications over the course of 8 months. The
sample was reduced to 3368 \StageOne candidates; these were then refined to
yield a sample that we expect to be over 90\%
complete and 20\% pure. We
comment on the scalability of the \SW system to the wide field survey era.

\end{abstract}

@@

Adopting the online \StageOne analysis, and the offline \StageTwo analysis, we
show in \Fref{fig:results:sample:CP} a plot of the more familiar (to
astronomers) quantities of completeness versus purity, again for
the two stages. As in \Fref{fig:results:sample:roc}, the detection threshold
varies along the curves. Completeness is defined as the number of correctly
detected sims divided by the total number of sims in the training set, while
purity is the number of correct detections divided by the total number of
detections.\footnote{The completeness is equivalent to the TPR and is also
known elsewhere as the ``recall.''  The purity is also known as the
``precision.''} If the training set samples from the same systems as the test
set, then the completeness of the training set will be equivalent to the
completeness of the test set. The purity depends on the proportion of sims to
duds, and so the purity of the test set must be approximated by rescaling the
training set to the expected proportion of lens systems to not-lens systems in
the survey. First we compute the expected number of false positives by
multiplying the FPR by the expected number of non-lenses in the survey. Then
we multiply the TPR by the expected number of lenses in the survey, to get the
expected number of true positives. The sum of the true positives and the false
positives gives the expected sample size; dividing the expected number of true
positives by this sample size gives the purity. Note that the completeness is
invariant to this transformation.
The \StageOne curves are truncated by the retirement of subjects in this phase,
which sets the minimum size of this sample. We see from the solid blue curve
that over 90\% completeness was reached, albeit in a sample with around 20\%
purity.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table*}
\begin{center}
\caption{Total crowd and subject sample properties from the \cfhtls project.}
\label{tab:crowd:contributions}
\begin{tabular}{cccccccc}
  \hline
  % \hline {Stage} & Subjects & Contribution                          & Agents & Skill      & Classifications          & Candidates & Information \\
  %                & $\Ns$    & $\sum_k^{\Nv} \contribution_k$ (bits) & $\Nv$  & $\sum_k^{\Nv} \skill_k$ (bits) & $\sum_k^{\Nv} \thiseffort$ & $\Ncands$  & $\sum_j^{\Ns}\sum_k^{\Nv} \information_{j,k}$ (bits) \\
  % \hline
  %           1    & $427064$ & $1292016.3$ & $36982$ & $1471.9$ & $10802125$ & $3368$ & $91122.6$ \\
  %           2    & $3679$   &   $21895.8$ &  $1964$ &  $102.4$ &   $224745$ &   $90$ &  $1640.4$ \\
  \hline {Stage} & Subjects & Contribution                          & Agents & Skill      & Classifications          & Candidates & Information \\
                           & $\Ns$    & $\sum_k^{\Nv} \contribution_k$ (bits) & $\Nv$  & $\sum_k^{\Nv} \skill_k$ (bits) & $\sum_k^{\Nv} \thiseffort$ & $\Ncands$  & $\sum_j^{\Ns}\sum_k^{\Nv} \information_{j,k}$ (bits) \\
            \hline
                      1    & $427064$ & $1292016.3$ & $36982$ & $1471.9$ & $10802125$ & $3368$ & $91122.6$ \\
                      2    & $3679$   &   $21895.8$ &  $1964$ &  $102.4$ &   $224745$ &   $90$ &  $1640.4$ \\
  \hline \hline
\end{tabular}
\medskip\\
\end{center}
\end{table*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\item Participation levels were high (over 36,000 volunteers, contributing
classifications at rates between $10^3$ and $10^4$ images per hour), suggesting
that if this can be maintained, visual inspection of tens of thousands of images
could be performed on timescales of weeks.

@@

\item The ``skill'' of the volunteers correlates strongly with the number of
images they have classified.  Quantifying the ``contribution'' as the integrated
skill over the test subjects  classified, we find that about 90\% of the
contribution was made by a few  hundred volunteers -- but that the width of the
skill distribution means that a  few thousand volunteers could have made
comparable contributions, had they classified more images.

\item The optimal true positive rate (completeness) and false positive rate in
the training set were estimated to be around $91--93\%$ and $<1\%$ (Stages 1 and
2). This FPR translates to an approximate purity of 20\%.

>>>>

We describe \SW, a novel gravitational lens discovery service that yields
samples of high purity and completeness through crowd-sourced visual inspection.
Carefully produced colour composite images are displayed to volunteers via a
classification interface which records their estimates of the positions of
candidate lensed features. Simulated lenses, and expert-classified images which
lack lenses, are inserted into the image stream at random intervals; this
training set is used to give the volunteers feedback on their performance, as
well as to calibrate it in order to allow dynamical updates to the probability
of any image they classify to contain a lens. Low probability systems are
retired from the site periodically, concentrating the sample towards a set of
candidates. Having divided 160 square degrees of Canada-France-Hawaii Telescope
Legacy Survey (\cfhtls) imaging into some 430,000 overlapping 84 by 84 arcsecond
tiles and displaying them on the site, we were joined by around 37,000
volunteers who contributed 11~million image classifications over the course of 8
months. The sample was reduced to 3368 \StageOne candidates; these were then
refined to yield a sample that we expect to be over 90\% complete and 30\% pure.
We comment on the scalability of the \SW system to the wide field survey era,
based on our finding that searches of $10^5$ images can be performed by a
crowd of $10^5$ volunteers in 6 days.
\end{abstract}

@@

Adopting the online \StageOne analysis, and the offline \StageTwo analysis, we
show in \Fref{fig:results:sample:CP} a plot of the more familiar (to
astronomers) quantities of completeness versus purity, again for
the two stages. As in \Fref{fig:results:sample:roc}, the detection threshold
varies along the curves. Completeness is defined as the number of correctly
detected sims divided by the total number of sims in the training set, while
purity is the number of correct detections divided by the total number of
detections.\footnote{The completeness is equivalent to the TPR and is also
known elsewhere as the ``recall.''  The purity is also known as the
``precision.''} If the training set samples from the same systems as the test
set, then the completeness of the training set will be equivalent to the
completeness of the test set. The purity depends on the proportion of sims to
duds, and so the purity of the test set must be approximated by rescaling the
training set to the expected proportion of lens systems to not-lens systems in
the survey. First we compute the expected number of false positives by
multiplying the FPR by the expected number of non-lenses in the survey. Then
we multiply the TPR by the expected number of lenses in the survey, to get the
expected number of true positives. The sum of the true positives and the false
positives gives the expected sample size; dividing the expected number of true
positives by this sample size gives the purity. Note that the completeness is
invariant to this transformation.
The \StageOne curves are truncated by the retirement of subjects in this phase,
which sets the minimum size of this sample. We see from the solid blue curve
that over 90\% completeness was reached, albeit in a sample with 30\%
purity.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table*}
\begin{center}
\caption{Total crowd and subject sample properties from the \cfhtls project.}
\label{tab:crowd:contributions}
\begin{tabular}{cccccccc}
  \hline
  % \hline {Stage} & Subjects & Contribution                          & Agents & Skill      & Classifications          & Candidates & Information \\
  %                & $\Ns$    & $\sum_k^{\Nv} \contribution_k$ (bits) & $\Nv$  & $\sum_k^{\Nv} \skill_k$ (bits) & $\sum_k^{\Nv} \thiseffort$ & $\Ncands$  & $\sum_j^{\Ns}\sum_k^{\Nv} \information_{j,k}$ (bits) \\
  % \hline
  %           1    & $427064$ & $1292016.3$ & $36982$ & $1471.9$ & $10802125$ & $3368$ & $91122.6$ \\
  %           2    & $3679$   &   $21895.8$ &  $1964$ &  $102.4$ &   $224745$ &   $90$ &  $1640.4$ \\
  \hline {Stage} & Subjects & Contribution                          & Agents & Skill      & Classifications          & Candidates & Information \\
                           & $\Ns$    & $\sum_k^{\Nv} \contribution_k$ (bits) & $\Nv$  & $\sum_k^{\Nv} \skill_k$ (bits) & $\sum_k^{\Nv} \thiseffort$ & $\Ncands$  & $\sum_j^{\Ns}\sum_k^{\Nv} \information_{j,k}$ (bits) \\
            \hline
                      1    & $427064$ & $1292016.3$ & $36982$ & $1471.9$ & $10802125$ & $3368$ & $91122.6$ \\
                      2    & $3679$   &   $21895.8$ &  $1964$ &  $102.4$ &   $224745$ &   $89$ &  $1640.4$ \\
  \hline \hline
\end{tabular}
\medskip\\
\end{center}
\end{table*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\item Participation levels were high (over 36,000 volunteers, contributing
classifications at rates between $10^3$ and $10^4$ images per hour), suggesting
that if this can be maintained, visual inspection of tens of thousands of images
could be performed just a few weeks. An expanded crowd of $10^6$ volunteers
(which has already been reached in the Galaxy Zoo project) would
be able to inspect a plausible sample of $10^6$ LSST or Euclid targets
on similar time scales.

@@

\item The ``skill'' of the volunteers correlates strongly with the number of
images they have classified.  Quantifying the ``contribution'' as the integrated
skill over the test subjects classified, we find that about 90\% of the
contribution was made by a few hundred volunteers ($1\%$ of the crowd) -- but
that the width of the skill distribution means that a  few thousand volunteers
could have made comparable contributions had they classified more images.

\item The optimal true positive rate (completeness) and false positive rate in
the training set were estimated to be around $91--93\%$ and $<1\%$ (Stages 1 and
2). This FPR translates to an approximate purity of 30\%. We find a
higher purity at \StageTwo (perhaps as a result of the least visible candidates already
being discarded): here, 100\% purity was reached at just under $90\%$
completeness. Because \SW is a supervised learning system, these numbers should
be taken to be upper limits to what we should expect for real lenses (which have
not been selected for a high visibility training set).
